Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Improve: conformity

It is difficult to make a new way of working stick in a large organization.
Use of agile can be rooted into the organization by creating an agile community.
Founding of interest groups and arranging regular seminars are good ways for
building community. As agility emphasizes people centricity and flexibility the
new ways of working can not be mandated. Instead, coaching should be applied for
leading the change. Several studies suggest conformity in the application of
agile models. Conformity avoids disorder when several teams are simultaneously
finding their agile ways.

>>>>

It is difficult to make a new way of working stick in a large organization.
Use of agile can be rooted into the organization by creating an agile community.
Founding of interest groups and arranging regular seminars are good ways for
building community. As agility emphasizes people centricity and flexibility the
new ways of working can not be mandated. Instead, coaching should be applied for
leading the change. Several studies suggest demanding conformity in the
application of agile practices. Agreeing on a common way of working avoids
disorder when several teams are simultaneously finding their agile ways.
